---
title: "lab_10_bailey"
author: "Allison Bailey"
date: "12/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
.
```{r}
# install packages
library(tidyverse)
library(gganimate)
library(magick)
library(janitor)
library(corrplot)
library(beepr)
library(stargazer)
library(praise)
library(transformr)
library(sf)
library(here)
```

### Objectives

- Multiple linear reression
- Check assumptions w/diagnositic plots
- Make predictons for MLR with new data
- Intro to maps in R & gganimate

### Multiple Linear Regression


```{r}

homes <- read_csv("slo_homes.csv")

homes_clean <- homes %>%
  clean_names() %>%
  filter(city %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande"))
```

Look at correlations between numeric variables (checking to see if we think that collinearity might be a concern)
```{r}
homes_cor <- cor(homes_clean[2:6])

homes_cor
```

Make a correlogram (plot of correlations)
```{r}
corrplot(homes_cor)
beep(20)
```

Let's start with a complete model:
```{r}
home_lm <- lm(price ~ city + bedrooms + bathrooms + sq_ft + status, data = homes_clean)

home_lm

# P = 184130.9 - 167396(Atascadero) + 31018(SLO) - 161645(bedrooms)
```
If everything else about the home is the same, then we would expect a home in Atascadero to sell for $167,396 dollars LESS than a home in Arroyo Grande, on average. 

```{r}
home_lm2 <- lm(price ~ city + sq_ft + status, data = homes_clean)
home_lm2
```

AIC values: 
```{r}
AIC(home_lm)
AIC(home_lm2)
```

```{r}
summary(home_lm)
summary(home_lm2)
```

Now I'm going to create a nice regression table with 'stargazer' :
```{r, results = 'asis'}
stargazer(home_lm, home_lm2, type = "html")

```

Now let's check out the diagnostic plots to see if our assumptions (normality of residulas and homoscedasticity) are satisfied or if we're really concerned.

- Linearly related variables
- Residuals normally distruted
- Variances constant
- Residulas iid (independent, uncorrelated)

```{r}
plot(home_lm2)
```
Make some home price predictions with new data

We're going to be using that simplified model (home_lm2)

- First, create some new data that contains city, sq_ft, status
- Give that new data to home_lm2 to make new predictions
- Plot it

```{r}

new_df <- data.frame(city = rep(c("San Luis Obispo", "Arroyo Grande", "Atascadero"), each = 10), 
                     sq_ft = rep(seq(0, 5000, length = 10)),
                     status = "Regular")
new_df
```

Use the 'predict()' to make new predicitons using home_lm2:
```{r}
predict_df <- predict(home_lm2, newdata = new_df)
predict_df

# Bind that together with the new_df:
full_df <- data.frame(new_df, predict_df)

full_df
```
Make a graph with the actuall data, and what our model actually predicts:
```{r}
ggplot() +
  geom_point(data = homes_clean,
             aes(x = sq_ft, y = price, color = city, pch = city)) +
  geom_line(data = full_df,
            aes(x = sq_ft, y = predict_df, color = city)) +
  theme_light()

ggplot(data = homes_clean, aes(x= sq_ft, y = price)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~city)
```

### Intro to the sf packages

'sf' = simple features

Sticky geometries! Which means we can just work with attributes like a normal data frame for wrangling, viz, etc. 

Get CA dams data:

```{r}
dams <- read_csv("ca_dams.csv") %>%
  clean_names() %>%
  drop_na(latitude) %>%
  drop_na(longitude) %>%
  drop_na(year_completed)


```

Convert lat/lon numbers to simple features data (sf)
```{r}
dams_sf <- st_as_sf(dams, coords = c("longitude", "latitude"))
st_crs(dams_sf) <- 4326

plot(dams_sf)
```

Now, lets read n the shapefile data for the state of CA (outer boundary TIGER shapefile data)

```{r}
ca_border <- read_sf(here::here("ca_state_border"), layer = "CA_State_TIGER2016")

plot(ca_border)
```

Now, plot dams n CA over the top of the CA outline:

```{r}
ggplot() +
  geom_sf(data = ca_border, fill = "red") +
  geom_sf(data = dams_sf, aes(size = dam_height, color = county), alpha = 0.5, show.legend = FALSE) +
  theme_minimal()




```

Making an animated plot:
```{r, include = FALSE, echo=FALSE}
ggplot() +
  geom_sf(data = ca_border) +
  geom_sf(data = dams_sf, size = 1.5, color = "gray50") +
  theme_void() +
  labs(title = 'Year: {round(frame_time, 0)}') +
  transition_time(year_completed) +
  shadow_mark(alpha = 1) 
```

